Put Title here

### 2018-06-12 General WLD combinatorics.tex
cyclic interval proof implemented, hopefully correctly this time.

%*****************
%Other useful mathematical operations and functions
\newcommand{\D}{\partial}
\newcommand{\rk}{\textrm{rk}}
\newcommand{\spn}{\textrm{span }}
\newcommand{\rd}{\textrm{d}}
\newcommand{\Res}{\textrm{Res}}
%*****************

@@

@@

\begin{enumerate}
\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $s$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$. Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$. Write $W = (\cP \setminus p, n)$.
\item If $Prop(i) = \emptyset$ do nothing.
\item Increment $i$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm} \note{I don't like how this is written. Any ideas?}

\begin{prop}\label{res:alg k labels}
If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop} \note{is there a way to do this theorem using the chords and polygons?}
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$. In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$. Suppose this doesn't happen, i.e. there is a propagator $p_0 \in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.  We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.

Fix an $a \in [n]$. Write $V_{p_0} = (i_{p_0},i_{p_0}+1,j_{p_0},j_{p_0}+1)$ with $a \leq_a i_{p_0} <_a j_{p_0}$.

Since $p$ is not removed by step $j_{p_0}+1$, there are $4$ propagators $q_1, r_1, s_1, t_1$ that are removed at step $i_{p_0},i_{p_0}+1,j_{p_0}$ , or $j_{p_0}+1$ respectively, allowing $p_0$ to remain after $n$ steps. Let us consider the propagators $s_1$ and $t_1$, preventing $p_0$ from being eliminated at steps $b_0$ and $b_0+1$. Let $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$, where \bas i_{p_0} <_a i_{t_1} <_a i_{s_1} < j_{s_1} \leq_a j_{t_1} = j_{p_0}\;.\eas Note that $j_{r_1}$ must either be $j_{p_0}-1$ or $j_{p_0}$. Otherwise, it would not be removed at the $j_{p_0}^{th}$ step. Admissibility prevents $i_{p_0} = i_{t_1}$ as this would imply that both $p_0 = (i_{p_0}, j_{p_0})$ and $t_1 = (i_{p_0}, j_{p_0})$.

In order for $t_1$ and $s_1$ to be removed at step $j_{p_0}$ and $j_{p_0}+1$ respectively, they cannot be removed at steps $i_{t_1}$ and $i_{t_1} +1$ or $i_{s_1}$ and $i_{s_1}+1$ respectively. Therefore, there needs to be two pairs of propagators, $q_2$, $r_2$ which are removed at step $i_{s_1}$ and $i_{s_1}+1$, and $q_3$, $r_3$ which are removed at step $i_{t_1}$ and $i_{t_1}+1$. Note that this implies that $i_{p_0}+2 <_a i_{t_1}$. Otherwise, there is not room to place both the propagators $q_3$, $r_3$.

For each $q_m$ and $r_m$ thus identified, there must be other pairs of propagators, $p_{m'}$ and $q_{m'}$ (with $m'> m$) that are removed at steps $i_{q_m}$ and $i_{q_m} +1$ or $i_{r_m}$ and $i_{r_m}+1$. Note that under this construction, $i_{r_m} <_a i_{q_m}$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction ($p_k \in \{q_k, r_k, s_k, t_k\}$, or $k=0$).

 \begin{description}
\item[$i_{r_m} = i_{p_k}+2$] Then there is not room to place both the propagators $q_{m'}$, and $r_{m'}$. Thus $r_m$ is removed at the step $i_{r_m} + 1$. Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
 \item[$i_{r_m} = i_{p_k}+1$] Then there is not room to place either the propagators $q_{m'}$, and $r_{m'}$. Thus $r_m$ is removed at the step $i_{r_m}$. Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
 \item[$i_{r_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $q_m$ is not removed at $i_{q_m}$ or $i_{q_m}+1$. By the above argument, there exists an $r_{m'}$ such that $i_{r_m'} = i_{r_m}$. This requires the existence of propagators that that $q_m'$ is not removed at $i_{q_m'}$ or $i_{q_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{q_m} - i_{r_m}-1$ propagators can be supported on the cyclic interval $\{i_{r_m}, i_{q_m}+1\}$.
 \end{description}

\todo{can this be simplified? Does it just need a picture?}

\begin{comment}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
\end{comment}
\end{proof}

Infact, we have proved more than the fact that each propagator contributes to the $I_a$ by the $n^{th}$ step. We have shown the each vertex $v \in V_p$ is contributed to some $I_{a_{p,v}}$ by $p$ for some $a_{p,v} \in [n]$

\begin{cor}\label{every vertex contributed cor}
For each propagator $p \in \cP$, and vertex $v \in V_p$, there is an $a_{p,v}$ such that $p$ contributes $v$ to $I_{a_{p,v}}$.
\end{cor}

@@

Suppose $p$ never contributed $j$ via Algorithm \ref{alg:put GN on WLD}. There there would be at least one propagator $s_1 = (i_{s_1}, j_{s_1})$ that contributed $j$ for all vertices $a \in [n]$. The vertex $j_{s_1} \in \{j, j-1\}$. Then there would have to be propagators $q_2$, $r_2$ that contributed $i_{s_1}$ and $i_{s_2}$ for all $a \in [n]$. But this is would create the need for an infinite number of propagators in a finite Wilson Loop diagram, which is impossible.

The same argument holds for $j+1$, except that one has to add the existence of a second propagator $t_1 = (i_{t_1}, j)$ to the construction above.

By cyclic symmetry, this is sufficient to prove that $p$ must also contribute $i$ and $i+1$ at some point.

For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram. Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$. Furthermore, for any $p = (i, j) \in \cP$, write $\cP_{i,j} =  \{ q = (i_q, j_q)\in \cP | i \leq_i i_q <_i j_q \leq_i j\}$ to be the set of propagators supported on the cyclic interval $[i, j]$. Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$. Note that $p = \cP_{i,j} \cap \cP_{j,i}$.

@@

\begin{cor} \label{rightmost prop last cor}
Given any Wilson loop diagram, $W = (\cP, n)$, and $p = (i,j) \in \cP$, consider the subdiagrams $W_L  = (\cP_{i,j}, n)$ and $W_R = (\cP_{j,i}, n)$. Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
\end{cor}

\begin{proof}
Consider $W_L$. Since every propagator in a Wilson loop diagram must contribute to $I_{i+2}^{W_L}$, it remains to check that no propagator can contribute after $p$. This could only happen if there were a different propagator, $q$ with an endpoint on edge $i$. If $q = (i , i+2)$, then it would be the first propagators to be removed, with contribution $i+2$. If it $q = (i, l)$, with $l > i+2$, then it would contribute either $l$ or $l+1$. Otherwise, one would need the existence of an infinite set of other propagators, as above.

A similar argument works for $W_R$.
\end{proof}

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, there is a cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
\end{lem}

\begin{proof}

>>>>

%*****************
%Other useful mathematical operations and functions
\newcommand{\D}{\partial}
\newcommand{\rk}{\textrm{rk }}
\newcommand{\spn}{\textrm{span }}
\newcommand{\rd}{\textrm{d}}
\newcommand{\Res}{\textrm{Res}}
%*****************

@@

\title{Put Title here}
%\author{}
%\date{}

@@

\begin{enumerate}
\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
\item While $\cP \neq \emptyset$, perform the following steps.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$. Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$. Write $W = (\cP \setminus p, n)$.
\item If $Prop(i) = \emptyset$ do nothing.
\item Increment $i$ by 1 and repeat from (a).
\end{enumerate}
\end{enumerate}
\end{algorithm} \note{I don't like how this is written. Any ideas?}

If the propagator $p$ is removed at vertex $i$ according to the algorithm for $I_a$, we say that $p$ \emph{contributes} $i$ to $I_a$.

Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas

\begin{dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$. One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$. Furthermore, $a-3 <_{v+1} s_m$. Similarly, for the given $a$, either $a-3 <_{v+1} i_{s_4}$ or there exist $2$ propagators $s_5$ and $s_6 \in P_w$ such that $s_5 = (i_{s_5}, i_{s_4})$ and $s_6 = (i_{s_6}, i_{s_4})$. One may also have $s_6 = (i_{s_6}, i_{s_4}-1)$. Furthermore, $a-3 <_w s_m$.
\end{enumerate}
\end{dfn}

\begin{comment}
\begin{dfn}
Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex. For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$) an edge of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} defined as follows: \begin{enumerate}
\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
\item The sets $P_v$ and $P_w$ are disjoint. 
\item There is an $r \in P_{v}$ such that $j_r \in \{v, v-1\}$ and $ i_r \in [i_p, j_p]$. If $j_r = v-1$, then $r$ is the clockwise most propagator on the edge $v$. Similarly, there is a $r \in P_{w}$ such that $j_r =v$ and $ i_r \in [i_p, j_p]$.
\item For every $q = (i_q, j_q) \in P_{v}$, or $P_w$, if there are at least two propatagors $s$ and $t$ $\in \cP$ satisfying $s = (i_s, i_q)$ or $s = (i_s, i_q-1 )$ (in which case $s$ is the clockwise most propagator on the edge $i_q$) and $t = (i_t, i_t)$ then all such $s$ and $t$ are also in $P_v$ or $P_w$. These are called the daughter propagators of $q$. If two such propagators don't exist, then $q$ is called a terminal propagator. 
\item For the $a$ given above, there is a propagator $q$ with a set of daughters $\{s_m\}$ satisfying $a-3 <_{v+1} i_{s_m}$.
\end{enumerate} 
\end{dfn}
\end{comment}

\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex. If there exists a $P_v$, for $v \in \{i,j\}$, then $p$ does not contribute $v$ to $I_a$. If there are two sets $P_v$ and $P_w$, for $w \in \{i+1, j+1\}$, then $p$ does not contribute $w$ to $I_a$. 
\end{lem}

\begin{proof}
We consider first the case of $p$ not contributing $v$ to $I_a$.

The set $P_v$ is constructed such that, $s_1$ if it exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ to $I_a$. By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ before vertex $v$ or $v-1$, or it encounters it at $i_{s_1}$.  In this case, the existence of $s_2$ and $s_3$ prevent $s_1$ from contributing at vertices $i_{s_1}$ or $i_{s_1}+1$. Therefore, $s_1$ remains in the diagram at step $v$.

If both $P_v$ and $P_w$ exists, then if $s_1$ and $s_3$ exist at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ and $w$ to $I_a$. By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ and $s_4$ before vertex $v$ or $v-1$, or it encounters only $s_1$ before $v$ or $v-1$. By the above argument, $s_1$ remains in the diagram at step $v$. Finally, the algorithm may encounter $s_4$ at $i_{s_4}$. In this case, the existence of $s_5$ and $s_6$ prevent $s_4$ from contributing at vertices $i_{s_4}$ or $i_{s_4}+1$. Therefore, $s_4$ remains in the diagram at step $v$.   Thereofre, in this case, $p$ cannot contribute either $v$ or $v+1$ to $I_a$.
\end{proof}

There is an easy corrollary to this, describing when propagators cannot contribute certain vertices to elements of the Grassman necklace.

\begin{cor} \label{protecting cor}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$. If $a \in [j_p+1, i_p+1]$ then no protecting set $P_v$ or $P_w$ can protect $p$ at $v$ or $v+1$ from $a$.
\end{cor}

\begin{proof}
Since $W$ is admissible, it cannot have crossing propagators. Therefore niether $P_v$ cannot have the requisite propagator $s$ with $a-3 <_{v+1} i_s$.
\end{proof}

\begin{comment}
\begin{lem}\label{protecting lem}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$. Then $p$ does not contribute $i$ or $j$ to $I_a$ if there is a subtree protecting $i$ or $j$ from $a$ in $\tau(W)$. Furthermore, $p$ does not contribute $i+1$ or $j+1$ if there are two protecting subtrees, at least one of which has a leaf vertex at $v$.
\end{lem}

\begin{proof}
It is sufficient to prove this for $i$ and $i+1$. The other two can be proved by switching the roles of $i$ and $j$. We show this by contradiction.

Assume that $p$ does not contribute $i$ to $I_a$. Furthermore, that there is a binary tree $T$ protecting $p$ at $i$ from $a$. Then, there is some propagator $q= (i_q, j_q) \in \cP$ corresponding to a leaf of $T$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$. Further, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$. Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.

In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.

For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$. Note that under this construction, $i_{t_m} <_j i_{s_m}$. By construction, each of these propagators must have endpoints in $[a,i] \cap [j,i]$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k$ is the first propagator of $T$ lying counterclockwise from $a$.).

 \begin{description}
\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m} + 1$. Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
 \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m}$. Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$. By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$. This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
 \end{description}

Since all of these cases lead to a contradiction, one cannot both have $p$ not contribute $j$ to $I_a$ and not have a binary tree $T$ protecting $p$ at $j$ from $a$.

The argument for $j+1$ is the same with two trees, $T_1$ and $T_2$, one leaf of $T_1$ preventing $p$ from contributing $j$ to $I_a$, and the corresponding leaf of $T_2$ preventing $p$ from contributing $j+1$.

The converse, howevever requires an extra condition.

\begin{lem} \label{protect conv lem}
For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$, $w \in \{i+1, j+1\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp. $w$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp. neither $P_v$ nor $P_w$) does not exsist, then $p$ contributes $v$ (resp. $w$) to $I_a$.
\end{lem}

\begin{proof}
If $p$ doesn't contribute $v$ or $w$ $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator at $s_1$ preventing $p$ from contributing $v$ (or $w$) to $I_a$, or there is a pair of propagators $s_1$ (resp. and $s_4$) preventing $p$ from contributing $w$, or $v$, at $I_a$.

If there is a propagator $s_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$ with $j_{s_1} \in \{v, v-1\}$), then $s_1$ did not contribute $i_{s_1}$ or $i_{s_1} +1 $ to $I_a$. Therefore, $s_1$ cannot contribute $i_{s_1}$ $i_{s_1}+1$ to $I_a$. In other words, either $a-3 <_{v+1} i_{s_1}$ or there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $s_3 = (i_{s_3}, j_{s_3})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_3} <_{s_1} i_{s_2} <_{s_1} j_{s_2} \leq_{s_1} j_{s_3} = j_{s_1}$ that prevent this. We show that, if $a-3 \not <_{v+1} i_{s_1}$, then $a-3 <_{v+1} i_{s_2} <_{v+1} s_3$. That is, there is a set $P_v$ preventing $p$ from contributing $v$.

The argument for showing that there must be two sets $P_v$ and $P_w$ is simlar, and is not made explicit here.

We proceed by contradiction. Suppose $a-3 \not <_{v+1} i_{s_2}$. Then, there exists two propagators $s_4$ and $s_5$ such that $s_4 = (i_{s_4}, j_{s_4})$ and $s_5 = (i_{s_5}, j_{s_5})$, with $j_{s_4} \in \{i_{s_2}, i_{s_2}-1\}$ and $i_{s_5} <_{s_2} i_{s_4} <_{s_2} j_{s_4} \leq_{s_2} j_{s_5} = j_{s_2}$. If $a-3 <_{v+1} i_{s_4} <_{v+1} s_5$, we may assume without loss of generality that there are no futher propagators of the form $t = (i_t, j_t)$ with $j_t \in \{i_{s_1}, j_{s_1}-1\}$ or $i_t \in [ i_{s_4}, i_{s_1}]$. Otherwise, one may replace $p$ with $s_1$ in this argument. Therefore, $s_1$ contributes $i_{s_1}$ to $I_a$, which is a contradiction. Therefore, we must again suppose that $a-3 \not <_{v+1} i_{s_4}$.

In order for $s_1$ to exists at step $v$ of algorithm \ref{Alg:put GN on WLD}, one must continue to find pairs of propagators $s_{m'}$, $s_{m'+1}$ in $\cP$ that sheild the initial endpoint of a previously defined propagator, $s_m$. There are three cases to consider. Let $s_k$ indicate a propagator identified at an earlier stage of this construction where $i_{p_0} = \min{i_p, a}$.

 \begin{description}
\item[$i_{s_m} = i_{p_k}+2$] By admissibility, there is not room to place both the propagators $s_{m'}$, and $s_{m'+1}$. Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \item[$i_{s_m} = i_{p_k}+1$] By admissibility, there is not room to place either the propagators $s_{m'}$, or $s_{m'+1}$. Thus $s_m$ is removed at the step $i_{s_m}$. Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore neither is $s_{m'}$. Furthermore, there cannot be propagators that prevent $s_{m'}$ from being removed at $j_{s_m}$ or $j_{s_m}+1$. Otherwise, we could replace $p$ with $sm_{m'}$ and repeat this argument. Since $\cP$ is finite, this replacement process must terminate, forcing $s_{m'}$ to contribute $j_{s_m}$ or $j_{s_m}+1$, and thereby, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
 \end{description}
\end{proof}

\begin{comment}

\begin{lem}\label{useful lem for GN alg}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i, j) \in \cP$. Let $v$ be a vertex such that $i +1 \leq_i v \leq_i j$ (resp. $j +1 \leq_j v \leq_j i$). If there exists another propagator $q = (i_q, j_q)$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$, (resp. $j_q \in \{j, j-1\}$ and $i +1 \leq_i i_q \leq_i j$), then $q$ contributes $m_v$ to $I_v$, where $m_v \in \{j, j+1\}$, (resp. $m_v \in \{i, i+1\}$).
\end{lem}

\begin{proof}
In this proof, we consider the case where $i +1 \leq_i v \leq_i j$. The situation when $j +1 \leq_j v \leq_j i$ is similarly proved by exchanging the roles of $i$ and $j$.

Suppose the statement doesn't hold. Then, for some propagator $q= (i_q, j_q) \in \cP$ such that $i_q \in \{i, i+1\}$ and $j +1 \leq_j j_q \leq_j i$, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$. Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.

In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.

For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$. Note that under this construction, $i_{t_m} <_j i_{s_m}$.

There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k = p$).

 \begin{description}
\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m} + 1$. Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
 \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$. Thus $t_m$ is removed at the step $i_{t_m}$. Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
 \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$. Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$. By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$. This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$. This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
 \end{description}

\begin{cor} \label{useful cor for GN alg}
The above lemma also holds for $v = j+1$ (resp. $v = i+1$, unless $q = (i-1, j)$ (resp. $q = (j-1, i)$).
\end{cor}
\begin{proof}
The proof is exactly as above. This statement is not included in the statement of the previous lemma only out of concerns for linguistic clarity.
\end{proof}
\end{comment}

We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}. 
\begin{prop}\label{res:alg k labels}
If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop} 
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$. In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$. Suppose this doesn't happen, i.e. there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$. Without loss of generality, assume $a \leq_a i <_a j$. Otherwise, change the roles of $i$ and $j$.

Since $p$ is not removed by step $j+1$, by Lemma \ref{protect dfn lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.

However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
\end{proof}
\begin{comment}
such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.

@@

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.

\end{proof}
\end{comment}

\begin{lem} \label{vertex cyclic int lem}
For every $v \in V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
\end{lem}

@@

Let $k_1 \ldots k_r$ be the set of propagators ending on edge $j$ or $j-1$, ordered such that $k_1$ is the first propagators clockwise from $p$, and $k_r$ is the clockwisemost propagator on edge $j-1$. For each $k_x$, write $P_{x} = \{k_x, s_x, t_x\}$, where $s_x$ and $t_x$, if they  exist, to be the two clockwise most propagators preventing $k_x$ from contributing $j$ to $I_{i+2}$. Similarly, let $l_1 \ldots l_m$ be the set of propagators ending on edge $i$ or $i-1$, ordered such that $l_1$ is the first propagators clockwise from $p$, and $l_m$ is the clockwisemost propagator on edge $i-1$. For each $l_y$, write $Q_{y} = \{l_x, s_y, t_y\}$, where $s_y$ and $t_y$, if they  exist, to be the two clockwise most propagators preventing $l_y$ from contributing $i$ to $I_{j+2}$.

Define $b_1 = \min{k_1+1, s_1+1}$. We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$. (If $b_1 <_{j+1} i+2$ then this interval is empty.) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}. Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $b_1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range. If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$. In this case, we say $b_1= j$.

Define $b_2 = \min{k_2+1, s_2+1}$. If $r > 1$, and $j_{k_2}=j$, for all $a \in [b_1+1, b_2]$ $p$ contributes $j+1$ to $I_a$. In this range, $P_1$ is a protective set for $p$ at $j$, but $P_2$ is not a protective set for $j+1$ in this range. Therefore, in this range, $j+1$ is the first vertex of $p$ without a protective set. If the stated condidtions do not hold, then $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.

Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$. Again, for all $a$ in this range, both $P_1$ and $P_2$ are protective sets of $p$ at $j$ and $j+1$. Furthermore, by Corrollary \ref{protect cor}, no set $Q_y$ can be a protective set for $p$ at $i$ or $i+1$ for $a$ in this range.

By switching the roles of $i$ and $j$, we see that for every element of $V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
\end{proof}

{\color{red}For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram. Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$. Furthermore, for any $p = (i, j) \in \cP$, write $\cP_{i,j} =  \{ q = (i_q, j_q)\in \cP | i \leq_i i_q <_i j_q \leq_i j\}$ to be the set of propagators supported on the cyclic interval $[i, j]$. Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$. Note that $p = \cP_{i,j} \cap \cP_{j,i}$.}

@@

\begin{cor} \label{rightmost prop last cor}
Given any Wilson loop diagram, $W = (\cP, n)$, and $p = (i,j) \in \cP$, consider the subdiagrams $W_L  = (\cP_{i,j}, n)$ and $W_R = (\cP_{j,i}, n)$. Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
\end{cor} \todo{do you need this}

{\color{red}\begin{proof}
The support vertices of $p$, $V_p = \{i, i+1, j, j+1\}$ are the last four vertices supporting any propagators at all in the $<_{i+2}$ linear order on $[n]$. Since $p$ contributes to $I_{i+2}^{W_L}$, it must contribute at one of these $4$ vertices.

The only possible configuration in which this result cannot hold is if $i$ or $i+1$ were in $I_{i+2}^{W_L}$ but not contributed by $p$.

\end{proof}}\todo{currently rubbish}
